Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-06 paper/tex/paper.tex
Update paper.tex

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
% \usepackage{fancyhdr}
\usepackage{svg}
\usepackage{comment}
\usepackage{float}
\usepackage[font=small,skip=0pt]{caption}

\usepackage{biblatex}
\addbibresource{paper.bib}

@@

We introduce \textit{Litrepl}, a text processor that employs the following
approaches: first, utilizing straightforward bidirectional text streams for
inter-process communication with language interpreters to evaluate code; second,
advocating for the reuse of existing text document formats. In both the Markdown
and \LaTeX\ evaluators we have implemented, simplified parsers are used to
distinguish code and result sections from the rest of the document. As of now,
we support Python and Shell interpreter families, as well as a custom large
language model communication interpreter. Finally, we strive to leverage
POSIX\cite{POSIX2024} operating system facilities as much as possible.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{hyperref}
% \usepackage{fancyhdr}
\usepackage{svg}
\usepackage{comment}
\usepackage{float}
\usepackage[font=small,skip=0pt]{caption}
\usepackage{biblatex}
\addbibresource{paper.bib}
\usepackage[para,bottom]{footmisc}

@@

We introduce
\textit{Litrepl}\footnote{\url{https://github.com/sergei-mironov/litrepl}},
a text processor that employs the following approaches: first, utilizing
straightforward bidirectional text streams for inter-process communication with
language interpreters to evaluate code; second, advocating for the reuse of
existing text document formats. In both the Markdown and \Latex evaluators we
have implemented, simplified parsers are used to distinguish code and result
sections from the rest of the document.  As of now, we support Python and Shell
interpreter families, as well as a custom large language model communication
interpreter. Finally, we strive to leverage POSIX\cite{POSIX2024} operating
system facilities as much as possible.
